### 2017-07-07 paper/compositional.tex
fixed issue with \vec{\lem}

\begin{definition}
An $n$-dimensional measurable map $\vec{\lem}=(\lem_1,\dots,\lem_n)$ is an NC supermartingale (NCSM) for a program $\program$ supported by an invariant map $\inv$ if there exists $\eps>0$ such that:
\begin{compactenum}
	\item  for each $1\leq i \leq n$, $\lem_i$ is non-negative in each location of $\pCFG_{\program}$;
	\item 
	$\vec{\lem}$ is $\eps$-$\inv$-ranking in each location $\loc\in\slice{(\program)}$; and
	\item 
	for each $1\leq i \leq n$, $\lem_i$ is
	unaffected in each $\loc\in\loops(\program)$.
\end{compactenum}
An $n$-dimensional linear NCSM (LinNCSM) is an $n$-dimensional NCSM which is also a linear expression map.
\end{definition}

>>>>

\begin{definition}
An $n$-dimensional measurable map $\overrightarrow{\lem}=(\lem_1,\dots,\lem_n)$ 
is an NC supermartingale (NCSM) for a program $\program$ supported by an 
invariant map $\inv$ if there exists $\eps>0$ such that:
\begin{compactenum}
	\item  for each $1\leq i \leq n$, $\lem_i$ is non-negative in each location of $\pCFG_{\program}$;
	\item 
	$\overrightarrow{\lem}$ is $\eps$-$\inv$-ranking in each location 
	$\loc\in\slice{(\program)}$; and
	\item 
	for each $1\leq i \leq n$, $\lem_i$ is
	unaffected in each $\loc\in\loops(\program)$.
\end{compactenum}
An $n$-dimensional linear NCSM (LinNCSM) is an $n$-dimensional NCSM which is also a linear expression map.
\end{definition}
